BVP Paper

### 2017-11-28 tex/bvp_paper.tex
adds FC equations

\newcommand{\Div}[1]{\ensuremath{\nabla\cdot\left( #1\right)}}
\newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
\newcommand{\grad}{\ensuremath{\nabla}}
\newcommand{\RB}{Rayleigh-B\'{e}nard }
\newcommand{\stressT}{\ensuremath{\bm{\bar{\bar{\Pi}}}}}
\newcommand{\lilstressT}{\ensuremath{\bm{\bar{\bar{\sigma}}}}}
\newcommand{\nrho}{\ensuremath{n_{\rho}}}
\newcommand{\approptoinn}[2]{\mathrel{\vcenter{
	\offinterlineskip\halign{\hfil$##$\cr
	#1\propto\cr\noalign{\kern2pt}#1\sim\cr\noalign{\kern-2pt}}}}}

@@

\section{Experiment} 
\label{sec:experiment}
\subsection{Incompressible, Boussinesq \RB Convection}
In studies of convection, it is natural to nondimensionalize the flows on the freefall velocity.
Under the Boussinesq approximation, where $\rho = \rho_0 (1 - \alpha T_1)$ on the gravitational term in the momentum
equation and $\rho = \rho_0$ on all other terms, the freefall velocity is $v_{\text{ff}} = \sqrt{\alpha g L^2 (dT/dz)_0}$.
where $L$ is the depth of the domain, $g$ is the gravitational acceleration, and $(dT/dz)_0$ is the initial temperature
gradient of the atmosphere, which controls the flux through the system.  The typical timescale and length scale
then relate to each other according to $t_{\text{ff}} = L/v_{\text{ff}}$.
Under this nondimensionalization, the Boussinsq, incompressible equations of motion are
\begin{gather}
\Div{\bm{u}} = 0, 
	\label{eqn:incompressible}
\\
\frac{\partial \bm{u}}{\partial t} + \bm{u}\cdot\grad\bm{u} =
-\grad\varpi + T_1\hat{z} + \frac{\text{Pr}}{\text{Ra}}\grad^2\bm{u}, 
	\label{eqn:bouss_momentum_eqn}
\\
\frac{\partial T_1}{\partial t} + \bm{u}\cdot\grad(T_0 + T_1) = \frac{1}{\text{Pr}\,\text{Ra}}\grad^2 T_1,
	\label{eqn:bouss_energy_eqn}
\end{gather}
where
\begin{equation}
\text{Ra} = \frac{g \alpha L^4 \left(\frac{dT}{dz}\right)_0}{\nu\chi} = \frac{(L\,v_{\text{ff}})^2}{\nu\chi}, \qquad \text{Pr} = \frac{\nu}{\chi}
\end{equation}
are the nondimensional Rayleigh and Prandtl numbers, where $\nu$ is the viscous diffusivity and $\chi$ is
the thermal diffusivity.

@@

@@

\appendix
\section{Process for setting enthalpy flux}

>>>>

\newcommand{\Div}[1]{\ensuremath{\nabla\cdot\left( #1\right)}}
\newcommand{\DivU}{\ensuremath{\nabla\cdot\bm{u}}}
\newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
\newcommand{\grad}{\ensuremath{\nabla}}
\newcommand{\RB}{Rayleigh-B\'{e}nard }
\newcommand{\stressT}{\ensuremath{\bm{\bar{\bar{\Pi}}}}}
\newcommand{\lilstressT}{\ensuremath{\bm{\bar{\bar{\sigma}}}}}
\newcommand{\nrho}{\ensuremath{n_{\rho}}}
\newcommand{\approptoinn}[2]{\mathrel{\vcenter{
	\offinterlineskip\halign{\hfil$##$\cr
	#1\propto\cr\noalign{\kern2pt}#1\sim\cr\noalign{\kern-2pt}}}}}

@@

\section{Experiment} 
\label{sec:experiment}
\subsection{Incompressible, Boussinesq \RB Convection}
In studies of convection, it is natural to nondimensionalize the flows on the freefall velocity.
Under the Boussinesq approximation, where $\rho = \rho_0 (1 - \alpha T_1)$ on the gravitational term in the momentum
equation and $\rho = \rho_0$ on all other terms, the freefall velocity is $v_{\text{ff}} = \sqrt{\alpha g L^2 (dT/dz)_0}$.
where $L$ is the depth of the domain, $g$ is the gravitational acceleration, and $(dT/dz)_0$ is the initial temperature
gradient of the atmosphere, which controls the flux through the system.  The typical timescale and length scale
then relate to each other according to $t_{\text{ff}} = L/v_{\text{ff}}$.
Under this nondimensionalization, the Boussinsq, incompressible equations of motion are
\begin{gather}
\DivU = 0, 
	\label{eqn:incompressible}
\\
\frac{\partial \bm{u}}{\partial t} + \bm{u}\cdot\grad\bm{u} =
-\grad\varpi + T_1\hat{z} + \frac{\text{Pr}}{\text{Ra}}\grad^2\bm{u}, 
	\label{eqn:bouss_momentum_eqn}
\\
\frac{\partial T_1}{\partial t} + \bm{u}\cdot\grad(T_0 + T_1) = \frac{1}{\text{Pr}\,\text{Ra}}\grad^2 T_1,
	\label{eqn:bouss_energy_eqn}
\end{gather}
where
\begin{equation}
\text{Ra} = \frac{g \alpha L^4 \left(\frac{dT}{dz}\right)_0}{\nu\chi} = \frac{(L\,v_{\text{ff}})^2}{\nu\chi}, \qquad \text{Pr} = \frac{\nu}{\chi}
\end{equation}
are the nondimensional Rayleigh and Prandtl numbers, where $\nu$ is the viscous diffusivity and $\chi$ is
the thermal diffusivity.

@@

\subsection{Fully Compressible Convection}
We study stratified convection in an ideal gas whose adiabatic index is $\gamma = 5/3$.
The initial atmospheric stratification is polytropic \cite{anders&brown2017}.
We assume a Newtonian radiative conduction term \cite{lecoanet&all2014}, and solve the
fully compressible Navier-Stokes equations of the form
\begin{gather}
\frac{\partial \ln \rho}{\partial t} + \bm{u}\cdot\grad\ln\rho + \DivU = 0
	\label{eqn:FC_continuity}
\\
\frac{D \bm{u}}{Dt} = -T\grad\ln\rho - \grad T + \bm{g} - \Div{\stressT}
	\label{eqn:FC_momentum}
\\
\frac{D T}{D t} + (\gamma-1)T\DivU = 
\frac{1}{\rho c_V}\left(\kappa\grad^2 T - [\stressT\cdot\grad]\cdot\bm{u}\right),
	\label{eqn:FC_energy}
\end{gather}
where $D/Dt \equiv \partial/\partial t + \bm{u}\cdot\grad$ and the viscous stress
tensor is defined as
\begin{equation}
\Pi_{ij} \equiv -\mu\left(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij
}\DivU\right)
\label{eqn:stress_tensor}
\end{equation}
and $\delta_{ij}$ is the Kronecker delta function.

@@

\appendix
\section{Table of Boussinesq Runs}

\section{Table of stratified runs}
